% Analysis

# Packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(gsheet)
library(ggthemes)
library(lme4)
library(agricolae)
library(emmeans)
library(car)
library(cowplot)
```

# Screening isolates

## Load data

```{r}
pre_data =  gsheet2tbl("https://docs.google.com/spreadsheets/d/1ROxKsXD8DKcdVIletmxKK2dG6O_IA3Bz83uwh-QY8gU/edit?usp=sharing")
head(pre_data)
```

```{r}

pre_data %>% 
  filter(time_dai== max(time_dai)) %>%
  group_by(tratamento) %>% 
  summarise(median_sev = median(sev, na.rm = T)) %>% 
  arrange(median_sev)
```


## Selected isolates

```{r}
selecionados = c( "UCBV03", "UCBV05", "UCBV06", "UCBV07", "UCBV17", "UCBV38", "UCBV97", "UCBV101", "UCBV133")
```
## Visualization
```{r}

pre_data %>% 
  mutate(selecao = case_when(tratamento %in% selecionados ~ "Selected",
                     !tratamento %in% selecionados ~ "Non-selected")) %>% 
  
  mutate(tratamento = case_when(tratamento == "alter" ~ "Check",
                                tratamento != "alter" ~ tratamento)) %>% 
  filter(time_dai== max(time_dai)) %>% 
  na.omit() %>% 
  ggplot(aes(reorder(tratamento,-sev), sev, color = selecao))+
  geom_jitter(shape = 1, alpha  =0.7, width = 0.1)+
  geom_boxplot(alpha = 0.5, size = 0.5)+
  scale_color_manual(values= c("gray", "black"))+
  theme_minimal_hgrid()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "top")+
  labs(x= "", y="Final severity (%)", color = "")
  ggsave("figs/screeningbox.png", dpi = 600, height = 4, width = 8)
```



# Biocontrol assays

## Loading data

```{r}
potato = gsheet2tbl("https://docs.google.com/spreadsheets/d/1h3ZZH9nx-nlmS4VKRXEOKq3cnxVa7gK1ExqZgyHqWm4/edit?usp=sharing") %>% 
  filter(!trat %in% c("UCBV07+17", "UCBV07+133")) %>% 
  filter(study != 4)
head(potato)
```


## Final severity 

```{r}
sev_f %>% 
  ungroup() %>% 
  mutate(study2 = case_when(study == 1 ~"First trial",
                              study == 2 ~"Second trial",
                              study == 3 ~"Third trial"
                              )) %>% 
  
  ggplot(aes(reorder(trat, sev, FUN = median), sev))+
  geom_jitter( shape = 1, alpha = 0.8, width = 0.1)+
  geom_boxplot(alpha = 0.5)+
  facet_wrap(~study2, scales = "free_x")+
  theme_minimal_hgrid()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(x="", y = "Final severity (%)")

ggsave("figs/box.png", dpi = 600, height = 4, width = 10)
```

## Modeling: Mix effect linear model

```{r}
lme1 = lmer(log(sev) ~ trat + (1|study), data = sev_f)
summary(lme1)
```


ANOVA
```{r}
Anova(lme1)
```


```{r}
emms <-  emmeans(lme1, "trat", type = "response")
plot(emms, comparisons = T)
```

```{r message=FALSE, warning=FALSE}
CLD(emms, Letters = letters)
```


## Control efficacy

```{r}
confi = confint(lme1)[-c(1,2),]
data.frame(emms) %>% 
  select(trat) %>% 
  mutate(logC = as.matrix(summary(lme1)$coefficients[,1]),
         se = round(as.matrix(summary(lme1)$coefficients[,2]),4),
         mean = round((1-(exp(as.matrix(summary(lme1)$coefficients[,1]))))*100,2)) %>% 
  mutate(CL = round((1-exp(confi[,2]))*100,2),
         CU = round((1-exp(confi[,1]))*100,2)) %>% 
  filter(trat != "CHECK") 
```

## Control efficacy
```{r}
confi = confint(lme1)[-c(1,2),]
data.frame(emms) %>% 
  select(trat) %>% 
  mutate(mean = 1-(exp(as.matrix(summary(lme1)$coefficients[,1])))) %>% 
  mutate(CL = 1-exp(confi[,1]),
         CU = 1-exp(confi[,2])) %>% 
  filter(trat != "CHECK") %>% 
  ggplot(aes(reorder(trat,mean), mean*100))+

  geom_point(size = 2)+
  geom_errorbar(aes(ymin =CU*100, ymax = CL*100 ), width = 0.2,
                position = position_dodge(width = 0.2))+
  scale_color_calc()+
  labs(x = "",
       y ="Control efficacy (%)",
       color ="")+
  theme_bw()+
  theme(legend.position = "bottom")+
  coord_flip()

ggsave("figs/effficacy.png", dpi = 600, height = 6, width = 4)
```





# Esporulation assays

##Loading and Tidying data

```{r}
alt_spor = gsheet2tbl("https://docs.google.com/spreadsheets/d/1h3ZZH9nx-nlmS4VKRXEOKq3cnxVa7gK1ExqZgyHqWm4/edit#gid=1690024692") %>% 
  filter(!trat %in% c("UCBVUCBV07+17","UCBV07+133","")) %>% 
  filter(study != 4) %>% 
  mutate(trat = case_when(trat == "Control"~"CHECK",
                          trat != "Control"~trat))
```

```{r}
alt_long = alt_spor%>% 
  gather(4:5, key = "state", value = "count") %>% 
  separate(state, into = c("state", "fungi"), sep = "_") %>% 
  mutate(state = factor(state, levels = c("Before drying", "After drying")))%>% 
  mutate(count = round( ((count*100)/0.004)/1.9625 ),0 )

alt_long
```


```{r}
clo_spor = gsheet2tbl("https://docs.google.com/spreadsheets/d/1h3ZZH9nx-nlmS4VKRXEOKq3cnxVa7gK1ExqZgyHqWm4/edit#gid=387958184")%>% 
  filter(!trat %in% c("133+7","7+17")) %>% 
  filter(study != 4)
```

```{r}
clo_long = clo_spor%>% 
  gather(4:5, key = "state", value = "count") %>% 
  separate(state, into = c("state", "fungi"), sep = "_") %>% 
  mutate(state = factor(state, levels = c("Before drying", "After drying"))) %>% 
  mutate(count = round(((count*100)/0.00025)/1.9625) ,0)
```


```{r}
full_long = alt_long %>% 
  bind_rows(clo_long)
full_long
```

## visualization

```{r}
full_long %>% 
  ggplot(aes(trat, count))+
  geom_jitter()+
  facet_grid(fungi~state, scales = "free_y")+
  theme_minimal_hgrid()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

## Modeling Alternaria sporulation

```{r}
 glm1 = glmer(count ~ trat*state + (1|study), family = poisson, data = alt_long)
summary(glm1)
```

```{r}
Anova(glm1)
```

```{r}
emmip(glm1, trat ~state)
```

trat dentro do state
```{r}
emms_spo1 <-  emmeans(glm1, "trat", by = "state")
```

```{r}
plot(emms_spo1, comparisons = T, adjust = "tukey")
```

```{r}
CLD(emms_spo1, Letters = letters)
```

state dentro do trat


```{r}
emms_spo2 <-  emmeans(glm1, "state", by = "trat")
# pairs(emms_spo2)
```
```{r}
plot(emms_spo2, comparisons = T, adjust = "tukey")
```
```{r}
CLD(emms_spo2, Letters = letters, reversed = T)
```

```{r}
data.frame(emms_spo2) %>% 
  mutate(esp = exp(emmean),
         lower.CL =exp(asymp.LCL),
         upper.CL =exp(asymp.UCL)) %>% 
  ggplot(aes(state, esp*10^-4, color = trat, group = trat))+
  
  geom_point(stat='summary', fun.y=sum, position = position_dodge(width = 0.2))+
  stat_summary(fun.y=sum, geom="line", position = position_dodge(width = 0.2))+
  
  
  geom_errorbar(aes(ymin =lower.CL*10^-4, ymax = upper.CL*10^-4 ), width = 0,
                position = position_dodge(width = 0.2))+
  scale_color_calc()+
  labs(x = "State",
       y = "Sporulation")+
  theme_bw()

```

```{r}
alt_plot = data.frame(emms_spo2) %>% 
  mutate(esp = exp(emmean),
         lower.CL =exp(asymp.LCL),
         upper.CL =exp(asymp.UCL)) %>% 
  ggplot(aes(trat, esp*10^-4, color = state,group = state))+
  geom_point(data = alt_long, aes(trat, count*10^-4, color = state),
             position = position_jitterdodge(dodge.width = 0.2),
             alpha = 0.1, shape = 1)+
  geom_errorbar(aes(ymin =lower.CL*10^-4, ymax = upper.CL*10^-4 ), width = 0.1,
                position = position_dodge(width = 0.2))+
  geom_point(position = position_dodge(width = 0.2))+
  scale_color_calc()+
  labs(x = "",
       y =expression(Conidia ~10^{4}/~cm^{2}),
       color ="")+
  theme_bw()+
  theme(legend.position = "bottom")
alt_plot
ggsave("figs/alt_esporulation.png", dpi = 600, height = 3, width = 7)
```


# Clonostachys sporulation
```{r}
 glm2 = glmer(count ~ trat*state + (1|study), family = poisson,data = clo_long)
summary(glm1)
```

```{r}
Anova(glm2)
```


```{r}
emms_spo_clo1 <-  emmeans(glm2, by ="state",  "trat")
```

```{r}
CLD(emms_spo_clo1, Letters = letters, reversed = T)
```


```{r}
emms_spo_clo2 <-  emmeans(glm2, "state", by = "trat")
# pairs(emms_spo_clo2)
```

```{r}
plot(emms_spo_clo2, comparisons = T, adjust = "tukey")
```

```{r}
CLD(emms_spo_clo2, Letters = letters, reversed = T)
```

```{r}
data.frame(emms_spo_clo2) %>% 
  mutate(esp = exp(emmean),
         lower.CL =exp(asymp.LCL),
         upper.CL =exp(asymp.UCL)) %>% 
  ggplot(aes(state, esp*10^-5, color = trat, group = trat))+
  
  geom_point(stat='summary', fun.y=sum, position = position_dodge(width = 0.2))+
  stat_summary(fun.y=sum, geom="line", position = position_dodge(width = 0.2))+
  
  
  geom_errorbar(aes(ymin =lower.CL*10^-5, ymax = upper.CL*10^-5 ), width = 0,
                position = position_dodge(width = 0.2))+
  scale_color_calc()+
  labs(x = "State",
       y = "Sporulation")+
  theme_bw()

```


```{r}
clo_plot = data.frame(emms_spo_clo1) %>% 
  bind_rows(data.frame(emms_spo2) %>% filter(trat == "CHECK") %>% 
              select(state,trat)) %>% 
  mutate(esp = exp(emmean),
         lower.CL =exp(asymp.LCL),
         upper.CL =exp(asymp.UCL)) %>% 
  ggplot(aes(trat, esp*10^-5, color = state, group = state))+
  geom_point(data = clo_long, aes(trat, count*10^-5, color = state),
             position = position_jitterdodge(dodge.width = 0.2),
             alpha = 0.1, shape = 1)+
  geom_point(position = position_dodge(width = 0.2))+
  geom_errorbar(aes(ymin =lower.CL*10^-5, ymax = upper.CL*10^-5 ), width = 0,
                position = position_dodge(width = 0.2))+
  scale_color_calc()+
  labs(x = "",
       y =expression(Conidia~10^{5}~mL^{-1}),
       color ="")+
  theme_bw()+
  theme(legend.position = "bottom")
clo_plot
ggsave("figs/clo_esporulation.png", dpi = 600, height = 3, width = 7)


```

```{r}
plot_grid(alt_plot+theme(legend.position = "none"),
          clo_plot, labels = "AUTO",
          nrow=2, rel_heights = c(0.85,1))

ggsave("figs/combo_spo.png", dpi = 600, height = 5, width = 7)
```

