% Analysis 

# Packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(gsheet)
library(ggthemes)
library(lme4)
library(agricolae)
library(emmeans)
library(car)
library(cowplot)
library(multcomp)
library(glmmTMB)
library(kableExtra)
library(patchwork)
```
```{r}
install.packages('TMB', type = 'source')
```

# Screening trial

```{r}
# 
pre_data =  gsheet2tbl("https://docs.google.com/spreadsheets/d/1ROxKsXD8DKcdVIletmxKK2dG6O_IA3Bz83uwh-QY8gU/edit?usp=sharing")
head(pre_data)
```

# Exploratory visualization

## Box plots

```{r}
selecionados = c("UCBV03", "UCBV05", "UCBV06", "UCBV07", "UCBV17", "UCBV38", "UCBV97", "UCBV101", "UCBV133")
pre_data %>%
  dplyr::select(-codes) %>% 
  mutate(selecao = case_when(tratamento %in% selecionados ~ "Selected",
                     !tratamento %in% selecionados ~ "Non-selected")) %>% 
  
  mutate(tratamento = case_when(tratamento == "alter" ~ "Control",
                                tratamento != "alter" ~ tratamento),
         time_dai =  as.factor(time_dai)) %>% 
  na.omit() %>%
  ggplot(aes(reorder(tratamento,-sev, mean), sev, color = time_dai ))+
  geom_point(shape = 1, alpha  =0.7, width = 0.1,
             position = position_jitterdodge())+
  geom_boxplot(alpha = 0.5, size = 0.5)+
  # scale_color
  # scale_color_manual(values= c("gray", "black"))+
  theme_minimal_hgrid()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "top")+
  labs(x= "", y="Final severity (%)", color = "")
  # ggsave("figs/screeningbox.png", dpi = 600, height = 4, width = 8)
```

```{r}
pre_data %>%

  mutate(selecao = case_when(tratamento %in% selecionados ~ "Selected",
                     !tratamento %in% selecionados ~ "Non-selected")) %>% 
  
  mutate(tratamento = case_when(tratamento == "alter" ~ "Control",
                                tratamento != "alter" ~ tratamento)) %>%
  na.omit() %>% 
  group_by(codes, time_dai) %>% 
  summarise(median = median(sev,na.rm=T),
            mean = mean(sev,na.rm=T)) %>% 
  filter(time_dai==5) %>% 
  arrange(mean)
```

## Plot means and medians

Treatments organized by the mean

```{r}
pre_data %>%

  mutate(selecao = case_when(tratamento %in% selecionados ~ "Selected",
                     !tratamento %in% selecionados ~ "Nonselected")) %>% 
  
  mutate(codes = case_when(tratamento == "alter" ~ "Control",
                                tratamento != "alter" ~ codes),
         time_dai =  as.factor(time_dai)) %>%
  na.omit() %>%
  ggplot()+
  geom_boxplot(aes(reorder(codes,-sev, mean), sev,
                   fill = time_dai),
               color = "gray20",
               outlier.size = .5,
               width = .5,
               alpha = 0.6,
               position = position_dodge(width = 0.5))+
  # geom_jitter(position = position_jitterdodge(jitter.width = 0.1))+
  stat_summary(aes(codes, sev, group = time_dai, shape= "Mean"),
                   fun = mean,
               geom = "point",
               size = 1.5,
               color = "red",
               position = position_dodge(width = 0.5))+
  theme_minimal_hgrid(font_size = 12)+
  scale_color_manual(name = "dd",values= c("black"))+
  scale_fill_manual(values= c("#3caea3", "#20639b"))+
  guides(shape = guide_legend(override.aes = list(size=3)))+
  labs(x= "",
       y= "Disease severity (%)",
       fill = "Days after inoc.", shape ="")+
  facet_grid(.~selecao, scales ="free_x",space = "free")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        panel.spacing = unit(2, "lines")
        #legend.position = "bottom"
        )

  ggsave("figs/screening.png", dpi = 600, height = 4, width = 10)
  ggsave("figs/screening.pdf", dpi = 600, height = 4, width = 10)

```


## Modeling
```{r}
data_screening = pre_data %>%
  mutate(selecao = case_when(tratamento %in% selecionados ~ "Selected",
                     !tratamento %in% selecionados ~ "Non-selected")) %>% 
  mutate(tratamento = case_when(tratamento == "alter" ~ "Control",
                                tratamento != "alter" ~ tratamento))%>%
  na.omit() %>% 
  filter(time_dai==5) %>% 
  mutate(sev = case_when(sev == 0 ~ 0.001,
                         sev != 0 ~ sev))
```

```{r}
scree_lm = lm(log(sev)~codes, data = data_screening)
as.data.frame(cld(emmeans(scree_lm, ~codes, transform = "response"), Letters = letters))
plot(emmeans(scree_lm, ~codes, transform = "response"))
```


# Confirmation trials

## Load data
```{r}
potato_df = gsheet2tbl("https://docs.google.com/spreadsheets/d/1h3ZZH9nx-nlmS4VKRXEOKq3cnxVa7gK1ExqZgyHqWm4/edit?usp=sharing") 
head(potato_df)
```

## Some data tidying

```{r}
potato = potato_df %>% 
  filter(!trat %in% c("UCBV07+17", "UCBV07+133")) %>% 
  filter(!study %in% c(1,4,5)) %>% 
  mutate(code = case_when(trat == "UCBV03" ~"pseud 1",
                          trat == "UCBV05" ~"pseud 2",
                          trat == "UCBV07" ~"chloro 1",
                          trat == "UCBV17" ~"chloro 2",
                          trat == "UCBV06" ~"rhiz 1",
                          trat == "UCBV38" ~"rhiz 2",
                          trat == "UCBV101" ~"roger 1",
                          trat == "UCBV97" ~"rosea 1",
                          trat == "UCBV133" ~"rosea 2",
                          trat == "CONT" ~"CONT",
                          trat == "FUNG" ~"FUNG"))
head(potato)
```


# Final severity and efficacy

## Prediction of final severity 

Here we (1) select severity data from the last day of evaluation; (2) set severity values equal to zero as 0.001 for futher log transformation; (3) calculate the mean for each replicate using the sev from each evaluated mean.

```{r}
sev_f = potato %>% 
  group_by(study) %>% 
  filter(dai == max(dai)) %>% 
  filter( !is.na(sev)) %>% 
  mutate(code = case_when(code == "CONT" ~ "Control",
                          code != "CONT" ~ code)) %>% 
  mutate(sev = case_when(sev == 0 ~ 0.001,
                         sev > 0~ sev)) %>% 
  group_by(study, code,trat, rep) %>% 
  summarise(sev = mean(sev)) 
sev_f
```

Here we change the name the trials (study) in the colunm

```{r}
ordem_code = c("Control", "FUNG", "chloro 2", "rhiz 2","chloro 1", "pseud 2","rosea 2",
"rhiz 1","roger 1","pseud 1","rosea 1")
sev_final =  sev_f %>% 
  ungroup() %>% 
  mutate(study = case_when(study == 2 ~"First trial",
                              # study == 2 ~"Second trial",
                              study == 3 ~"Second trial"
                              # study == 5 ~"Third trial"
                              )) %>% 
  mutate(code = factor(code,levels = ordem_code))
head(sev_final)
```

###  Visualization
Here we creat box plot with data from both trials
```{r}
sev_final %>% 
  ggplot(aes(reorder(code, sev, FUN = median), sev))+
  geom_jitter( shape = 1, alpha = 0.8, width = 0.1)+
  geom_boxplot(alpha = 0.5)+
  facet_wrap(~study, scales = "free_x")+
  theme_minimal_hgrid()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(x="", y = "Final severity (%)")

ggsave("figs/box.pdf", dpi = 600, height = 4, width = 7)
```

Data from spore concentration

```{r}
concentrat = gsheet2tbl("https://docs.google.com/spreadsheets/d/1SMCet9OEXwyLGnzmDGs2G1oDTdxamjcv1MkEg0v_B3U/edit?usp=sharing") %>% 
  group_by(trial, isolate) %>% 
  summarise(conc = mean(conc)) %>% 
  rename(code =isolate) %>% 
  mutate(trial = case_when(trial == 2 ~"First trial",
                            # study == 2 ~"Second trial",
                            trial == 3 ~"Second trial",
                            trial == 1 ~"screening"
                            )) %>% 
  rename(study =trial) %>% 
  filter(study != "screening")

```

### Effect of concentration on disease severity

```{r}
sev_final_conc = sev_final %>% 
  dplyr::select(study,code,sev) %>% 
  full_join(concentrat) %>%
  replace_na(list(conc=0))

```

```{r}
sev_final_conc %>% 
  ggplot(aes(conc,sev, color = code))+
  geom_point()+
  geom_smooth(method ="lm", se =F)
```

```{r}
lm_conc = lm(sev~conc, data = sev_final_conc %>% filter(study=="First trial"))
summary(lm_conc)
anova(lm_conc)
```

```{r}
lm_conc = lm(sev~conc, data = sev_final_conc %>% filter(study=="Second trial"))
summary(lm_conc)
anova(lm_conc)
```




## First trial
```{r}
sev_final_1 = sev_final %>% 
  dplyr::select(study,code,sev) %>% 
  full_join(concentrat) %>% 
  filter(study=="First trial") %>%
  replace_na(list(conc=0)) %>% 
  mutate(code = factor(code,levels = ordem_code))

```

### Model
```{r}
lm_f1 = lm(log(sev) ~ code, data = sev_final_1 )
summary(lm_f1)
```

#### ANOVA
```{r}
Anova(lm_f1)
```


```{r}
emms_f1 <-  emmeans(lm_f1, "code", type = "response")
```

#### Tukey


```{r message=FALSE, warning=FALSE}
cld(emms_f1, Letters = letters)
```


```{r}
confi = confint(lm_f1)
data.frame(emms_f1) %>% 
  dplyr::select(code) %>% 
  mutate(logC = as.matrix(summary(lm_f1)$coefficients[,1]),
         se = round(as.matrix(summary(lm_f1)$coefficients[,2]),4),
         P = round(as.matrix(summary(lm_f1)$coefficients[,4]),3),
         mean = round((1-(exp(as.matrix(summary(lm_f1)$coefficients[,1]))))*100,2)) %>% 
  mutate(CL = round((1-exp(confi[,2]))*100,2),
         CU = round((1-exp(confi[,1]))*100,2)) %>% 
  filter(code != "Control") %>% 
  arrange(-mean)
```

## Second trial
```{r}
sev_final_2 = sev_final %>% 
  dplyr::select(study,code,sev) %>% 
  full_join(concentrat) %>% 
  filter(study=="Second trial") %>%
  replace_na(list(conc=0)) %>% 
  mutate(code = factor(code,levels = ordem_code))

```

### Model
```{r}
lm_f2 = lm(log(sev) ~ code, data = sev_final_2 )
summary(lm_f2)
```
#### ANOVA
```{r}
Anova(lm_f2)
```


```{r}
emms_f2 <-  emmeans(lm_f2, "code", type = "response")
```

#### Tukey
```{r message=FALSE, warning=FALSE}
cld(emms_f2, Letters = letters)
```


```{r}
confi = confint(lm_f2)
data.frame(emms_f2) %>% 
  dplyr::select(code) %>% 
  mutate(logC = as.matrix(summary(lm_f2)$coefficients[,1]),
         se = round(as.matrix(summary(lm_f2)$coefficients[,2]),4),
         P = round(as.matrix(summary(lm_f2)$coefficients[,4]),3),
         mean = round((1-(exp(as.matrix(summary(lm_f2)$coefficients[,1]))))*100,2)) %>% 
  mutate(CL = round((1-exp(confi[,2]))*100,2),
         CU = round((1-exp(confi[,1]))*100,2)) %>% 
  filter(code != "Control") %>%  
  arrange(-mean)
```


```{r}
as.data.frame(emms_f1) %>% 
  bind_rows(
    as.data.frame(emms_f2),
    .id = "trial") %>% 
  mutate(study = case_when(trial == 1 ~"First trial",
                              trial == 2 ~"Second trial")) %>% 
  ggplot(aes(code,response, color=study))+
  
  geom_point(data = sev_final, 
             aes(reorder(code,sev),sev, fill = study),
             position = position_jitterdodge(jitter.width = 0.1,
                                             dodge.width = 0.4),
             color = "gray85")+
  
  geom_point(aes(code,response, color = study),
             position = position_dodge(width = 0.4),
             size = 3)+
  
  geom_errorbar(aes(code,ymin =lower.CL, ymax =upper.CL, color = study),
                width=0,size = 1,
                position = position_dodge(width = 0.4)) +
  
  scale_color_colorblind()+
  scale_x_discrete(guide = guide_axis(n.dodge = 2))+
  coord_cartesian(ylim=c(0,100))+
  theme_minimal_hgrid(font_size = 12)+
  labs(x = "", y= "Disease severity (%)", color = "", fill = "")

ggsave("figs/severity_sep.png", dpi = 600, height = 4, width = 7)
ggsave("figs/severity_sep.pdf", dpi = 600, height = 4, width = 7)
```



## Modelling final severity

```{r}
lm_sep12 = lmer(log(sev) ~ code*study +(1|study), data = sev_final )
summary(lm_sep12)
```

Anova
```{r}
Anova(lm_sep12)
```

Means prediction
```{r}
emms_sep12 <-  emmeans(lm_sep12, "code",by = "study", type = "response")
emms_sep12
```

#### Tukey mean comparison
```{r message=FALSE, warning=FALSE}
cld(emms_sep12, Letters = letters)
```

```{r}
cld(emmeans(lm_sep12, "study", by ="code"))
```

#### Final severity plot
```{r}
as.data.frame(emms_sep12) %>% 
  na.omit() %>% 
  mutate(upper.CL = case_when(upper.CL>100 ~100,
                              upper.CL<=100 ~upper.CL)) %>%
  ggplot()+
  
  geom_point(data = sev_final, 
             aes(reorder(code,sev),sev, fill = study),
             position = position_jitterdodge(jitter.width = 0.1,
                                             dodge.width = 0.4),
             color = "gray85")+
  
  geom_point(aes(code,response, color = study),
             position = position_dodge(width = 0.4),
             size = 3)+
  
  geom_errorbar(aes(code,ymin =lower.CL, ymax =upper.CL, color = study),
                width=0,size = 1,
                position = position_dodge(width = 0.4)) +
  
  scale_color_colorblind()+
  scale_x_discrete(guide = guide_axis(n.dodge = 2))+
  coord_cartesian(ylim=c(0,100))+
  theme_minimal_hgrid(font_size = 12)+
  labs(x = "", y= "Severity (%)", color = "", fill = "")

# ggsave("figs/severity_sep.png", dpi = 600, height = 4, width = 7)
# ggsave("figs/severity_sep.pdf", dpi = 600, height = 4, width = 7)
```


# AACPD

```{r}
# potato %>% 
#   ggplot(aes(as.numeric(dai), sev, color = as.factor(study),linetype = as.factor(leaf), group = rep))+
#   geom_point(position = position_dodge(0.5))+
#   geom_line()+
#   facet_wrap(study~code)
```

Correlation between final sev and AUDPC

```{r}
pf = potato %>% 
    na.omit() %>%
  group_by(study) %>% 
  filter(dai==max(dai)) %>% 
  group_by(trat, study, code) %>% 
  summarise(sev = mean(sev))

pauc = potato %>% 
  na.omit() %>% 
  group_by(trat,study,dai,rep,code) %>% 
  summarise(sev = mean(sev)) %>% 
  group_by(trat,study,rep,code) %>%
  summarise(audpc = audpc(sev,dai)) %>% 
  group_by(trat,study,code) %>% 
  summarise(audpc = mean(audpc))
  

cor(pf$sev, pauc$audpc)
plot(pf$sev, pauc$audpc)
```



# Sporulation 


```{r}
ordem_code2 = c("Control", "chloro 1","chloro 2", "pseud 1","pseud 2","rhiz 1","rhiz 2","roger 1", "rosea 1","rosea 2")

alt_spor = gsheet2tbl("https://docs.google.com/spreadsheets/d/1h3ZZH9nx-nlmS4VKRXEOKq3cnxVa7gK1ExqZgyHqWm4/edit#gid=1690024692") %>% 
  filter(!trat %in% c("UCBVUCBV07+17","UCBV07+133","")) %>% 
  filter(study != 4) %>% 
  mutate(trat = case_when(trat == "Control"~"CHECK",
                          trat != "Control"~trat))%>% 
  mutate(code = case_when(trat == "UCBV03" ~"pseud 1",
                          trat == "UCBV05" ~"pseud 2",
                          trat == "UCBV07" ~"chloro 1",
                          trat == "UCBV17" ~"chloro 2",
                          trat == "UCBV06" ~"rhiz 1",
                          trat == "UCBV38" ~"rhiz 2",
                          trat == "UCBV101" ~"roger 1",
                          trat == "UCBV97" ~"rosea 1",
                          trat == "UCBV133" ~"rosea 2",
                          trat == "CHECK" ~"Control"))
```



```{r}
alt_long = alt_spor%>% 
  gather(4:5, key = "state", value = "count") %>% 
  separate(state, into = c("state", "fungi"), sep = "_") %>%
  mutate(state = case_when(state=="Before drying"~"Fresh",
                           state=="After drying"~"Dried")) %>% 
  mutate(state = factor(state, levels = c("Fresh", "Dried")))%>%
  # mutate(state = factor(state, levels = c("Before drying", "After drying")))%>% 
  mutate(count = round( ((count*100)/0.004)/1.9625 ),0 )

alt_long
```


```{r}

clo_spor = gsheet2tbl("https://docs.google.com/spreadsheets/d/1h3ZZH9nx-nlmS4VKRXEOKq3cnxVa7gK1ExqZgyHqWm4/edit#gid=387958184")%>% 
  filter(!trat %in% c("133+7","7+17")) %>% 
  filter(study != 4)%>% 
  mutate(code = case_when(trat == "UCBV03" ~"pseud 1",
                          trat == "UCBV05" ~"pseud 2",
                          trat == "UCBV07" ~"chloro 1",
                          trat == "UCBV17" ~"chloro 2",
                          trat == "UCBV06" ~"rhiz 1",
                          trat == "UCBV38" ~"rhiz 2",
                          trat == "UCBV101" ~"roger 1",
                          trat == "UCBV97" ~"rosea 1",
                          trat == "UCBV133" ~"rosea 2",
                          trat == "CHECK" ~"Control"))
```

```{r}
clo_long = clo_spor%>% 
  gather(4:5, key = "state", value = "count") %>% 
  separate(state, into = c("state", "fungi"), sep = "_") %>% 
  mutate(state = case_when(state=="Before drying"~"Fresh",
                           state=="After drying"~"Dried")) %>%
  mutate(state = factor(state, levels = c("Fresh", "Dried")))%>% 
  # mutate(state = factor(state, levels = c("Before drying", "After drying"))) %>% 
  mutate(count = round(((count*100)/0.00025)/1.9625) ,0)
```





```{r}
full_long = alt_long %>% 
  bind_rows(clo_long) %>% 
  mutate(study = case_when(study == 2 ~"First trial",
                              # study == 2 ~"Second trial",
                              study == 3 ~"Second trial"
                              # study == 5 ~"Third trial"
                              ))
  
full_long
```




```{r}
full_long %>% 
  ggplot(aes(code, count, color = as.factor(study)))+
  geom_jitter(alpha = 0.2)+
  # geom_boxplot()+
  stat_summary()+
  facet_grid(fungi~state, scales = "free_y")+
  # scale_y_log10()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


```

# Effect of concentrations

```{r}
full_long_conc = full_long %>% 
  full_join(concentrat) %>% 
  replace_na(list(conc=0))

```
```{r}
full_long_conc %>% 
  ggplot(aes((conc),log(count+1)))+
  geom_point(aes(color =state))+
  geom_smooth(method = lm,aes(linetype=study))+
  facet_wrap(~fungi, scales = "free")

```




## Alternaria sporulation
```{r}
 glm1 = glmmTMB::glmmTMB(count ~  code*state +(code|study),
              data = alt_long,
              ziformula=~1,
              family=list(family="nbinom1",link="log")
              )
summary(glm1)

```

```{r}
Anova(glm1)
```



trat dentro do state
```{r}
emms_spo_alt1 <-  emmeans(glm1, "code", by = "state",transform = "response")
# pairs(emms_spo1)
```

```{r}
pairs(emms_spo_alt1)
```

```{r}
# cld(emms_spo_alt1, Letters = letters)
as.data.frame(cld(emms_spo_alt1, Letters = letters))
```



state dentro do trat


```{r}
emms_spo_alt2 <-  emmeans(glm1, "state", by = "code",transform = "response")
```

```{r}
as.data.frame(cld(emms_spo_alt2, Letters = letters, reversed = T))
```

```{r}
data.frame(emms_spo_alt2) %>% 
  # mutate(esp = exp(emmean),
  #        lower.CL =exp(asymp.LCL),
  #        upper.CL =exp(asymp.UCL)) %>% 
  ggplot(aes(state, response*10^-4, color = code, group = code))+
  
  geom_point(stat='summary', fun.y=sum, position = position_dodge(width = 0.2))+
  stat_summary(fun.y=sum, geom="line", position = position_dodge(width = 0.2))+
  
  
  geom_errorbar(aes(ymin =lower.CL*10^-4, ymax = upper.CL*10^-4 ), width = 0,
                position = position_dodge(width = 0.2))+
  scale_color_calc()+
  labs(x = "State",
       y = "Sporulation")+
  
  theme_bw()

```

## graph 1
```{r}
alt_plot = data.frame(emms_spo_alt2)%>% 
  mutate(code = factor(code,levels = ordem_code2)) %>%
  mutate(lower.CL = case_when(lower.CL<0 ~0,lower.CL>=0 ~lower.CL )) %>% 
  ggplot(aes(code, response*10^-4, group = state))+

  # geom_point(data = alt_long, aes(code, count*10^-4, fill = state),
  #            position = position_jitterdodge(dodge.width = 0.3, jitter.width = 0.1),
  #            alpha = 0.3, color = "gray")+
  
  geom_errorbar(aes(ymin =lower.CL*10^-4, ymax = upper.CL*10^-4, color = state), width = 00,
                position = position_dodge(width = 0.3), size =1)+
  
  geom_point(aes(color = state),position = position_dodge(width = 0.3),  size =3)+
  
  scale_color_calc()+
  scale_fill_calc()+
  coord_cartesian(ylim=c(0,5))+
    scale_x_discrete(guide = guide_axis(n.dodge = 2))+
  labs(x = "",
       title = "Alternaria grandis",
       y =expression(Conidia ~10^{4}/~cm^{2}),
       color ="")+
  theme_minimal_hgrid()+
  theme(legend.position = "none",
        plot.title = element_text(face = "italic", size =10))
alt_plot
# ggsave("figs/alt_esporulation.png", dpi = 600, height = 5, width = 7)
```


# Clonostachys sporulation
```{r}
 glm2 = glmmTMB::glmmTMB(count ~ code*state + (code|study),
                         family=list(family="nbinom1",link="log"),
                         ziformula = ~1,
                         data = clo_long)
summary(glm2)
```

```{r}
Anova(glm2)
```


```{r}
emms_spo_clo1 <-  emmeans(glm2, "code",by ="state",   transform="response")
```


```{r}
pairs(emms_spo_clo1)
```

```{r}
as.data.frame(cld(emms_spo_clo1, Letters = letters))
```


```{r}
emms_spo_clo2 <-  emmeans(glm2, "state", by = "code", transform="response")
# pairs(emms_spo_clo2)
```



```{r}
as.data.frame(cld(emms_spo_clo2, Letters = letters, reversed = T))
```

```{r}
data.frame(emms_spo_clo2) %>% 
 
  ggplot(aes(state,response*10^-5, color = code, group = code))+
  
  geom_point(stat='summary', fun.y=sum, position = position_dodge(width = 0.2))+
  stat_summary(fun.y=sum, geom="line", position = position_dodge(width = 0.2))+
  
  
  geom_errorbar(aes(ymin =lower.CL*10^-5, ymax = upper.CL*10^-5 ), width = 0,
                position = position_dodge(width = 0.2))+
  scale_color_calc()+
  labs(x = "State",
       y = "Sporulation")+
  theme_bw()

```


## graph 2

```{r}
clo_plot = data.frame(emms_spo_clo1) %>% 
  bind_rows(data.frame(emms_spo_alt2) %>% 
              filter(code == "Control") %>% 
               dplyr::select(state,code)) %>% 
  mutate(code = factor(code,levels = ordem_code2))%>% 

  ggplot(aes(code, response*10*10^-5,  group = state))+
  
  # geom_point(data = clo_long, aes(code, count*10*10^-5, fill = state),
  #            position = position_jitterdodge(dodge.width = 0.3, jitter.width = 0.1),
  #            alpha = 0.3, color = NA)+
  
  geom_errorbar(aes(ymin =lower.CL*10*10^-5, ymax = upper.CL*10*10^-5, color = state),
                width = 0,
                position = position_dodge(width = 0.3), size =1)+
  
  geom_point(position = position_dodge(width = 0.3), aes(color = state,), size =3)+
  
  scale_color_calc()+
  scale_fill_calc()+
  scale_x_discrete(guide = guide_axis(n.dodge = 2))+
  coord_cartesian(ylim = c(0,2000))+
  labs(x = "",
       title = expression(paste(italic("Clonostachys")," spp.")),
       y =expression(Conidia~10^{4}/~cm^{2}),
       color ="", fill = "")+
  theme_minimal_hgrid()+
  theme(legend.position = "bottom",
        plot.title = element_text(face = "italic", size =10)
        # axis.text.x = element_text(angle = 45, hjust = 1)
        )
clo_plot
# ggsave("figs/clo_esporulation.png", dpi = 600, height = 5, width = 7)


```


## Combo
```{r}
(alt_plot)/clo_plot+
   plot_annotation(tag_levels ="a")&
  theme()

ggsave("figs/combo_spo.png", dpi = 600, height = 7, width = 6.5)
ggsave("figs/combo_spo.pdf", dpi = 600, height = 7, width = 6.5)

```





